---
title: "Jun Pan DATA 607 wk7 Assignment"
author: "Jun Pan"
date: "October 13, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Assignment
Pick three of your favorite books on one of your favorite subjects.   At least one of the books should have more than one author.  For each book, include the title, authors, and two or three other attributes that you find interesting. Take the information that you've selected about these three books, and separately create three files which store the book's information in HTML (using an html table), XML, and JSON formats (e.g.  "books.html", "books.xml", and "books.json").  To help you better understand the different file structures, I'd prefer that you create each of these files "by hand" unless you're already very comfortable with the file formats. Write R code, using your packages of choice, to load the information from each of the three sources into separate R data frames.   Are the three data frames identical? Your deliverable is the three source files and the R code.  If you can, package your assignment solution up into an .Rmd file and publish to rpubs.com.  [This will also require finding a way to make your three text files accessible from the web]. 

Create tables in html, xml and json formate
firstly, I had my design of table in excel file; secondly, I manually wrote the codes in notepade ++ and saved on my computer in html, xml and json formate; then, I uploaded my html, xml and json files in my github reposition.
finally, I parsed all information by using r studio and read it.


The following on the detailed steps to get the data from github website.
-------------------------------------------------------------------------
```{r}
library(jsonlite)
library(XML)
library(knitr)
library(RCurl)
```

read html data from website
```{r}
raw_HTML = getURL("https://raw.githubusercontent.com/johnpannyc/Jun-Pan-DATA-607-wk7-assignment/master/bestnovels.html", ssl.verifypeer = FALSE)

bestnovels_HTML = readHTMLTable(raw_HTML, 
                           header = T, 
                           which=1, 
                           isHTML = TRUE, 
                           stringsAsFactors = F)
```

view the data frame
```{r}
kable(bestnovels_HTML)
```


read xml file from website
```{r}

raw_XML = getURL("https://raw.githubusercontent.com/johnpannyc/Jun-Pan-DATA-607-wk7-assignment/master/bestnovels1.xml", ssl.verifypeer = FALSE)
bestnovels_XML = xmlParse(raw_XML)
bestnovels_child = xmlChildren(bestnovels_XML)
head(bestnovels_child)

```


create a dateframe
```{r}
bestnovels_XML_df = data.frame()

bestnovels_XML_df = cbind(xpathSApply(bestnovels_XML, "//Title", xmlValue),
                     xpathSApply(bestnovels_XML, "//Author_1", xmlValue),
                     xpathSApply(bestnovels_XML, "//Author_2", xmlValue),
                     xpathSApply(bestnovels_XML, "//Year", xmlValue),
                     xpathSApply(bestnovels_XML, "//Price", xmlValue),
                     xpathSApply(bestnovels_XML, "//Language", xmlValue))
bestnovels_XML_df = data.frame(bestnovels_XML_df)
names(bestnovels_XML_df) = c("Title", "Author_1", "Author_2", "Year", "Price", "Language")
kable(bestnovels_XML_df)
```


read json file from website
```{r}
raw_JSON = getURL("https://raw.githubusercontent.com/johnpannyc/Jun-Pan-DATA-607-wk7-assignment/master/bestnovles1.json", ssl.verifypeer = FALSE)

bestnovels_JSON = fromJSON(txt = raw_JSON)

str(bestnovels_JSON)
```

create a dataframe
```{r}
bestnovels_JSON_df = as.data.frame(bestnovels_JSON)

kable(bestnovels_JSON_df)
```
  
